A Short Demo Article: Regression Models for Count Data in \proglang{R}

### 2022-06-21 5_artigos/journal-of-statistical-software/draft/draft-jss-lineu.tex
corrige texto, atualiza artigos

\documentclass[article]{jss}

@@

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
engine='R', tidy=FALSE
)
@

<<preliminaries, echo=FALSE, results='hide'>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

@@

\Address{
  Lineu Alberto Cavazani de Freitas\\
  Department of Informatics\\
  Paraná Federal University\\
  Centro Politécnico\\
  Curitiba 81531980, CP 19081, Paraná, Brazil.\\
  E-mail: \email{lineuacf@gmail.com}\\
  %URL: \url{https://www.zeileis.org/}
}

\begin{document}

@@

<<functions, echo=FALSE, message=FALSE, warning=FALSE, results='hide'>>=
library(mcglm)
library(Matrix)

#source('~/msc/0_funcoes/functions.R')
library(htmcglm)
@

@@

<<install-mcglm, eval=FALSE>>=
install.packages("mcglm")
library(mcglm)
@

@@

<<install-htmcglm, eval=FALSE>>=
library(devtools)
install_github("lineu96/htmcglm")
library(htmcglm)
@

@@

<<soya, message=FALSE, warning=FALSE, results='hide'>>=
data("soya", package = "mcglm")
@

@@

<<lin_pred>>=
form.grain <- grain ~ block + water * pot
form.seed <- seeds ~ block + water * pot

soya$viablepeasP <- soya$viablepeas / soya$totalpeas
form.peas <- viablepeasP ~ block + water * pot
@

@@

<<mat_pred>>=
Z0 <- mc_id(soya)
@

@@

<<fit, message=FALSE, results='hide'>>=
fit_joint <- mcglm(linear_pred = c(form.grain, 
                                   form.seed, 
                                   form.peas),
                   matrix_pred = list(c(Z0), 
                                      c(Z0), 
                                      c(Z0)),
                   link = c("identity",
                            "log", 
                            "logit"),
                   variance = c("constant", 
                                "tweedie", 
                                "binomialP"),
                   Ntrial = list(NULL, 
                                 NULL, 
                                 soya$totalpeas),
                   power_fixed = c(T,T,T),
                   data = soya)
@

@@

<<anovaI>>=
mc_anova_I(fit_joint)
@

@@

<<anovaII>>=
mc_anova_II(fit_joint)
@

@@

<<anovaIII>>=
mc_anova_III(fit_joint)
@

@@

<<manovaI>>=
mc_manova_I(fit_joint)
@

@@

<<manovaII>>=
mc_manova_II(fit_joint)
@

@@

<<manovaIII>>=
mc_manova_III(fit_joint)
@

@@

<<lin_hyp1>>=
mc_linear_hypothesis(object =  fit_joint, 
                     hypothesis = c('beta11 = 0'))
@

@@

<<lin_hyp2>>=
mc_linear_hypothesis(object =  fit_joint, 
                     hypothesis = c('beta11 = 0', 
                                    'beta12 = 0'))
@

@@

<<lin_hyp3>>=

mc_linear_hypothesis(object =  fit_joint, 
                     hypothesis = c('beta11 = beta21'))

@

@@

<<hunting, message=FALSE, warning=FALSE, results='hide'>>=
data("Hunting", package = "mcglm")
@

@@

<<hunting2, message=FALSE, warning=FALSE, results='hide'>>=
form.OT <- OT ~ METHOD * SEX
form.BD <- BD ~ METHOD * SEX

Z0 <- mc_id(Hunting)
Z1 <- mc_mixed(~ 0 + HUNTER.MONTH, data = Hunting)

fit <- mcglm(linear_pred = c(form.BD, form.OT),
             matrix_pred = list(c(Z0, Z1), 
                                c(Z0, Z1)),
             link = c("log", "log"), 
             variance = c("poisson_tweedie",
                          "poisson_tweedie"),
             offset = list(log(Hunting$OFFSET), 
                           log(Hunting$OFFSET)),
             data = Hunting)
@

@@

<<lin_hyp4>>=
mc_linear_hypothesis(object =  fit, 
                     hypothesis = c('tau11 = 0'))

@

@@

<<lin_hyp5>>=

mc_linear_hypothesis(object =  fit, 
                     hypothesis = c('tau11 = 0',
                                    'tau21 = 0'))
@

@@

<<lin_hyp6>>=
mc_linear_hypothesis(object =  fit,
                     hypothesis = c('tau12 = tau12'))
@

@@

<<anova_disp>>=
mc_anova_dispersion(fit,
                    p_var = list(c(0,1), c(0,1)),
                    names = list(c('tau10', 'tau11'),
                                 c('tau20', 'tau21')))
@

@@

<<manova_disp>>=
mc_manova_dispersion(fit,
                     p_var = c(0,1),
                     names = c('tau0', 'tau1'))
@

@@

<<multcomp>>=
mc_multcomp(object = fit,
            effect = list(c('METHOD', 'SEX'), 
                          c('METHOD', 'SEX')), 
            data = Hunting)
@

@@

<<mult_multcomp>>=
mc_mult_multcomp(object = fit, 
                 effect = c('METHOD', 'SEX'), 
                 data = Hunting)
@

>>>>

\documentclass[article]{jss}\usepackage[]{graphicx}\usepackage[]{xcolor}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

@@

\Address{
  Lineu Alberto Cavazani de Freitas\\
  Department of Informatics\\
  Paraná Federal University\\
  Centro Politécnico\\
  Curitiba 81531980, CP 19081, Paraná, Brazil.\\
  E-mail: \email{lineuacf@gmail.com}\\
  %URL: \url{https://www.zeileis.org/}
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{install.packages}\hlstd{(}\hlstr{"mcglm"}\hlstd{)}
\hlkwd{library}\hlstd{(mcglm)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\hlkwd{install_github}\hlstd{(}\hlstr{"lineu96/htmcglm"}\hlstd{)}
\hlkwd{library}\hlstd{(htmcglm)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{data}\hlstd{(}\hlstr{"soya"}\hlstd{,} \hlkwc{package} \hlstd{=} \hlstr{"mcglm"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{form.grain} \hlkwb{<-} \hlstd{grain} \hlopt{~} \hlstd{block} \hlopt{+} \hlstd{water} \hlopt{*} \hlstd{pot}
\hlstd{form.seed} \hlkwb{<-} \hlstd{seeds} \hlopt{~} \hlstd{block} \hlopt{+} \hlstd{water} \hlopt{*} \hlstd{pot}

\hlstd{soya}\hlopt{$}\hlstd{viablepeasP} \hlkwb{<-} \hlstd{soya}\hlopt{$}\hlstd{viablepeas} \hlopt{/} \hlstd{soya}\hlopt{$}\hlstd{totalpeas}
\hlstd{form.peas} \hlkwb{<-} \hlstd{viablepeasP} \hlopt{~} \hlstd{block} \hlopt{+} \hlstd{water} \hlopt{*} \hlstd{pot}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{Z0} \hlkwb{<-} \hlkwd{mc_id}\hlstd{(soya)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fit_joint} \hlkwb{<-} \hlkwd{mcglm}\hlstd{(}\hlkwc{linear_pred} \hlstd{=} \hlkwd{c}\hlstd{(form.grain,}
                                   \hlstd{form.seed,}
                                   \hlstd{form.peas),}
                   \hlkwc{matrix_pred} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwd{c}\hlstd{(Z0),}
                                      \hlkwd{c}\hlstd{(Z0),}
                                      \hlkwd{c}\hlstd{(Z0)),}
                   \hlkwc{link} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"identity"}\hlstd{,}
                            \hlstr{"log"}\hlstd{,}
                            \hlstr{"logit"}\hlstd{),}
                   \hlkwc{variance} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"constant"}\hlstd{,}
                                \hlstr{"tweedie"}\hlstd{,}
                                \hlstr{"binomialP"}\hlstd{),}
                   \hlkwc{Ntrial} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwa{NULL}\hlstd{,}
                                 \hlkwa{NULL}\hlstd{,}
                                 \hlstd{soya}\hlopt{$}\hlstd{totalpeas),}
                   \hlkwc{power_fixed} \hlstd{=} \hlkwd{c}\hlstd{(T,T,T),}
                   \hlkwc{data} \hlstd{= soya)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_anova_I}\hlstd{(fit_joint)}
\end{alltt}
\begin{verbatim}
## ANOVA type I using Wald statistic for fixed effects
## 
## Call: grain ~ block + water * pot
## 
##   Covariate Df       Chi Pr(>Chi)
## 1 Intercept 19 6283.6472    0e+00
## 2     block 18  419.6702    0e+00
## 3     water 14  405.1498    0e+00
## 4       pot 12  350.9316    0e+00
## 5 water:pot  8   30.4494    2e-04
## 
## Call: seeds ~ block + water * pot
## 
##   Covariate Df         Chi Pr(>Chi)
## 1 Intercept 19 127429.2620   0.0000
## 2     block 18    205.8174   0.0000
## 3     water 14    194.0161   0.0000
## 4       pot 12    130.2022   0.0000
## 5 water:pot  8     12.7366   0.1212
## 
## Call: viablepeasP ~ block + water * pot
## 
##   Covariate Df      Chi Pr(>Chi)
## 1 Intercept 19 971.1096   0.0000
## 2     block 18 300.2990   0.0000
## 3     water 14 297.4306   0.0000
## 4       pot 12 295.2420   0.0000
## 5 water:pot  8  20.0549   0.0101
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_anova_II}\hlstd{(fit_joint)}
\end{alltt}
\begin{verbatim}
## ANOVA type II using Wald statistic for fixed effects
## 
## Call: grain ~ block + water * pot
## 
##   Covariate Df      Chi Pr(>Chi)
## 1 Intercept  1 102.2961   0.0000
## 2     block  4  14.3051   0.0064
## 3     water 10  84.6677   0.0000
## 4       pot 12 350.9316   0.0000
## 5 water:pot  8  30.4494   0.0002
## 
## Call: seeds ~ block + water * pot
## 
##   Covariate Df       Chi Pr(>Chi)
## 1 Intercept  1 3993.9442   0.0000
## 2     block  4   11.6363   0.0203
## 3     water 10   70.8041   0.0000
## 4       pot 12  130.2022   0.0000
## 5 water:pot  8   12.7366   0.1212
## 
## Call: viablepeasP ~ block + water * pot
## 
##   Covariate Df      Chi Pr(>Chi)
## 1 Intercept  1  13.4353   0.0002
## 2     block  4   4.4305   0.3509
## 3     water 10  33.9928   0.0002
## 4       pot 12 295.2420   0.0000
## 5 water:pot  8  20.0549   0.0101
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_anova_III}\hlstd{(fit_joint)}
\end{alltt}
\begin{verbatim}
## ANOVA type III using Wald statistic for fixed effects
## 
## Call: grain ~ block + water * pot
## 
##   Covariate Df      Chi Pr(>Chi)
## 1 Intercept  1 102.2961   0.0000
## 2     block  4  14.3051   0.0064
## 3     water  2   2.3991   0.3013
## 4       pot  4  64.0038   0.0000
## 5 water:pot  8  30.4494   0.0002
## 
## Call: seeds ~ block + water * pot
## 
##   Covariate Df       Chi Pr(>Chi)
## 1 Intercept  1 3993.9442   0.0000
## 2     block  4   11.6363   0.0203
## 3     water  2    3.9399   0.1395
## 4       pot  4   19.1997   0.0007
## 5 water:pot  8   12.7366   0.1212
## 
## Call: viablepeasP ~ block + water * pot
## 
##   Covariate Df     Chi Pr(>Chi)
## 1 Intercept  1 13.4353   0.0002
## 2     block  4  4.4305   0.3509
## 3     water  2  5.2513   0.0724
## 4       pot  4 71.1026   0.0000
## 5 water:pot  8 20.0549   0.0101
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_manova_I}\hlstd{(fit_joint)}
\end{alltt}
\begin{verbatim}
## MANOVA type I using Wald statistic for fixed effects
## 
## Call: ~ block+water*pot
##   Covariate Df         Chi Pr(>Chi)
## 1 Intercept 57 168255.3139        0
## 2     block 54    816.7633        0
## 3     water 42    794.0601        0
## 4       pot 36    708.8164        0
## 5 water:pot 24     68.7879        0
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_manova_II}\hlstd{(fit_joint)}
\end{alltt}
\begin{verbatim}
## MANOVA type II using Wald statistic for fixed effects
## 
## Call: ~ block+water*pot
##   Covariate Df       Chi Pr(>Chi)
## 1 Intercept  3 5553.7954    0.000
## 2     block 12   23.7478    0.022
## 3     water 30  160.9564    0.000
## 4       pot 36  708.8164    0.000
## 5 water:pot 24   68.7879    0.000
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_manova_III}\hlstd{(fit_joint)}
\end{alltt}
\begin{verbatim}
## MANOVA type III using Wald statistic for fixed effects
## 
## Call: ~ block+water*pot
##   Covariate Df       Chi Pr(>Chi)
## 1 Intercept  3 5553.7954   0.0000
## 2     block 12   23.7478   0.0220
## 3     water  6    9.0173   0.1726
## 4       pot 12  149.0321   0.0000
## 5 water:pot 24   68.7879   0.0000
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_linear_hypothesis}\hlstd{(}\hlkwc{object} \hlstd{=  fit_joint,}
                     \hlkwc{hypothesis} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'beta11 = 0'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Linear hypothesis test
## 
## Hypothesis:            
## 1 beta11 = 0
## 
## Results:
##   Df    Chi Pr(>Chi)
## 1  1 1.2362   0.2662
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_linear_hypothesis}\hlstd{(}\hlkwc{object} \hlstd{=  fit_joint,}
                     \hlkwc{hypothesis} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'beta11 = 0'}\hlstd{,}
                                    \hlstr{'beta12 = 0'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Linear hypothesis test
## 
## Hypothesis:            
## 1 beta11 = 0
## 2 beta12 = 0
## 
## Results:
##   Df    Chi Pr(>Chi)
## 1  2 3.5639   0.1683
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_linear_hypothesis}\hlstd{(}\hlkwc{object} \hlstd{=  fit_joint,}
                     \hlkwc{hypothesis} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'beta11 = beta21'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Linear hypothesis test
## 
## Hypothesis:                 
## 1 beta11 = beta21
## 
## Results:
##   Df    Chi Pr(>Chi)
## 1  1 1.3491   0.2454
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{data}\hlstd{(}\hlstr{"Hunting"}\hlstd{,} \hlkwc{package} \hlstd{=} \hlstr{"mcglm"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{form.OT} \hlkwb{<-} \hlstd{OT} \hlopt{~} \hlstd{METHOD} \hlopt{*} \hlstd{SEX}
\hlstd{form.BD} \hlkwb{<-} \hlstd{BD} \hlopt{~} \hlstd{METHOD} \hlopt{*} \hlstd{SEX}

\hlstd{Z0} \hlkwb{<-} \hlkwd{mc_id}\hlstd{(Hunting)}
\hlstd{Z1} \hlkwb{<-} \hlkwd{mc_mixed}\hlstd{(}\hlopt{~} \hlnum{0} \hlopt{+} \hlstd{HUNTER.MONTH,} \hlkwc{data} \hlstd{= Hunting)}

\hlstd{fit} \hlkwb{<-} \hlkwd{mcglm}\hlstd{(}\hlkwc{linear_pred} \hlstd{=} \hlkwd{c}\hlstd{(form.BD, form.OT),}
             \hlkwc{matrix_pred} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwd{c}\hlstd{(Z0, Z1),}
                                \hlkwd{c}\hlstd{(Z0, Z1)),}
             \hlkwc{link} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"log"}\hlstd{,} \hlstr{"log"}\hlstd{),}
             \hlkwc{variance} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"poisson_tweedie"}\hlstd{,}
                          \hlstr{"poisson_tweedie"}\hlstd{),}
             \hlkwc{offset} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwd{log}\hlstd{(Hunting}\hlopt{$}\hlstd{OFFSET),}
                           \hlkwd{log}\hlstd{(Hunting}\hlopt{$}\hlstd{OFFSET)),}
             \hlkwc{data} \hlstd{= Hunting)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_linear_hypothesis}\hlstd{(}\hlkwc{object} \hlstd{=  fit,}
                     \hlkwc{hypothesis} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'tau11 = 0'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Linear hypothesis test
## 
## Hypothesis:           
## 1 tau11 = 0
## 
## Results:
##   Df     Chi Pr(>Chi)
## 1  1 22.5613        0
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_linear_hypothesis}\hlstd{(}\hlkwc{object} \hlstd{=  fit,}
                     \hlkwc{hypothesis} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'tau11 = 0'}\hlstd{,}
                                    \hlstr{'tau21 = 0'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Linear hypothesis test
## 
## Hypothesis:           
## 1 tau11 = 0
## 2 tau21 = 0
## 
## Results:
##   Df    Chi Pr(>Chi)
## 1  2 29.098        0
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_linear_hypothesis}\hlstd{(}\hlkwc{object} \hlstd{=  fit,}
                     \hlkwc{hypothesis} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'tau12 = tau12'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Linear hypothesis test
## 
## Hypothesis:               
## 1 tau12 = tau12
## 
## Results:
##   Df     Chi Pr(>Chi)
## 1  1 97.0998        0
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_anova_dispersion}\hlstd{(fit,}
                    \hlkwc{p_var} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,}\hlnum{1}\hlstd{),} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,}\hlnum{1}\hlstd{)),}
                    \hlkwc{names} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwd{c}\hlstd{(}\hlstr{'tau10'}\hlstd{,} \hlstr{'tau11'}\hlstd{),}
                                 \hlkwd{c}\hlstd{(}\hlstr{'tau20'}\hlstd{,} \hlstr{'tau21'}\hlstd{)))}
\end{alltt}
\begin{verbatim}
## ANOVA type III using Wald statistic for dispersion parameters
## 
## Call: BD ~ METHOD * SEX
## 
##   Dispersion Df     Chi Pr(>Chi)
## 1      tau10  1 22.5613        0
## 2      tau11  1 97.0998        0
## 
## Call: OT ~ METHOD * SEX
## 
##   Dispersion Df     Chi Pr(>Chi)
## 1      tau20  1  7.2008   0.0073
## 2      tau21  1 29.0133   0.0000
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_manova_dispersion}\hlstd{(fit,}
                     \hlkwc{p_var} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,}\hlnum{1}\hlstd{),}
                     \hlkwc{names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'tau0'}\hlstd{,} \hlstr{'tau1'}\hlstd{))}
\end{alltt}
\begin{verbatim}
## MANOVA type III using Wald statistic for dispersion parameters
## 
## Call: ~ METHOD*SEX
##   Covariate Df      Chi Pr(>Chi)
## 1      tau0  2  29.0980        0
## 2      tau1  2 124.2049        0
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_multcomp}\hlstd{(}\hlkwc{object} \hlstd{= fit,}
            \hlkwc{effect} \hlstd{=} \hlkwd{list}\hlstd{(}\hlkwd{c}\hlstd{(}\hlstr{'METHOD'}\hlstd{,} \hlstr{'SEX'}\hlstd{),}
                          \hlkwd{c}\hlstd{(}\hlstr{'METHOD'}\hlstd{,} \hlstr{'SEX'}\hlstd{)),}
            \hlkwc{data} \hlstd{= Hunting)}
\end{alltt}
\begin{verbatim}
## Multiple comparisons test for each outcome using Wald statistic
## 
## Call: BD ~ METHOD * SEX
## 
##                        Contrast Df      Chi Pr(>Chi)
## 1 Escopeta:Female-Escopeta:Male  1 175.7657        0
## 2 Escopeta:Female-Trampa:Female  1  20.1379        0
## 3   Escopeta:Female-Trampa:Male  1  35.6372        0
## 4     Escopeta:Male-Trampa:Male  1  24.3946        0
## 5   Trampa:Female-Escopeta:Male  1 217.7398        0
## 6     Trampa:Female-Trampa:Male  1 132.6125        0
## 
## Call: OT ~ METHOD * SEX
## 
##                        Contrast Df     Chi Pr(>Chi)
## 1 Escopeta:Female-Escopeta:Male  1 14.3969   0.0009
## 2 Escopeta:Female-Trampa:Female  1  6.5843   0.0617
## 3   Escopeta:Female-Trampa:Male  1  5.6455   0.1050
## 4     Escopeta:Male-Trampa:Male  1  0.7480   1.0000
## 5   Trampa:Female-Escopeta:Male  1 31.3069   0.0000
## 6     Trampa:Female-Trampa:Male  1 25.3203   0.0000
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{mc_mult_multcomp}\hlstd{(}\hlkwc{object} \hlstd{= fit,}
                 \hlkwc{effect} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{'METHOD'}\hlstd{,} \hlstr{'SEX'}\hlstd{),}
                 \hlkwc{data} \hlstd{= Hunting)}
\end{alltt}
\begin{verbatim}
## Multivariate multiple comparisons test using Wald statistic
## 
## Call: ~ METHOD*SEX
##                        Contrast Df      Chi Pr(>Chi)
## 1 Escopeta:Female-Escopeta:Male  2 215.0490        0
## 2 Escopeta:Female-Trampa:Female  2  31.8503        0
## 3   Escopeta:Female-Trampa:Male  2  47.8804        0
## 4     Escopeta:Male-Trampa:Male  2  27.5459        0
## 5   Trampa:Female-Escopeta:Male  2 287.6161        0
## 6     Trampa:Female-Trampa:Male  2 184.8844        0
\end{verbatim}
\end{kframe}
\end{knitrout}

### 2022-06-21 5_artigos/journal-of-statistical-software/template-revista/article-knitr.Rnw
corrige texto, atualiza artigos

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
\SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\begin{figure}[t!]
\centering
<<visualization, echo=FALSE, fig=TRUE, height=5.2, width=7>>=
par(mar = c(4, 4, 1, 1))
plot(table(quine$Days), xlab = "Days", ylab = "Frequency", axes = FALSE)
axis(2)
axis(1, at = 0:16 * 5, labels = FALSE)
axis(1, at = 0:8 * 10)
box()
@
\caption{\label{fig:quine} Frequency distribution for number of days absent
from school.}
\end{figure}

>>>>

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
engine='R', tidy=FALSE
)
@

<<preliminaries, echo=FALSE, results='hide'>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

@@

\begin{document}

@@

\begin{figure}[t!]
\centering
<<visualization, echo=FALSE, fig.height=5.2, fig.width=7>>=
par(mar = c(4, 4, 1, 1))
plot(table(quine$Days), xlab = "Days", ylab = "Frequency", axes = FALSE)
axis(2)
axis(1, at = 0:16 * 5, labels = FALSE)
axis(1, at = 0:8 * 10)
box()
@
\caption{\label{fig:quine} Frequency distribution for number of days absent
from school.}
\end{figure}
